Title

### 2019-05-09 paper_notes.Rmd
tested utility to check

$$
U=
\begin{cases}
\frac{x}{np}, & \text{if} \ x \leq np, \\
(2Z-M)+\frac{(M-Z)x}{p}, & otherwise
\end{cases}
$$

@@

$$
U=
\begin{cases}
\frac{x}{np}, & \text{if} \ x \leq np, \\
(2-M)+\frac{(M-1)x}{p}, & otherwise
\end{cases}
$$

The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 6 patches. With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results. To edit in table
^[Not managed to implement Flache's formula on slides, either not understood correctly what it would translate on my formula: p = n number of agents; f = P desired concentration.]

@@

f <- function(p,M,x,n){
  if (x  <= (n*p)){U <- (x/(n*p))}
  else {U <- (2-M) + (((M-1)*x)/(n*p))}
  round(U,digits = 3)
 # print(U)
}

@@

f0t6 <- f(0.5,0.6,0,6)
f1t6 <- f(0.5,0.6,1,6)
f2t6 <- f(0.5,0.6,2,6)
f3t6 <- f(0.5,0.6,3,6)
f4t6 <- f(0.5,0.6,4,6)
f5t6 <- f(0.5,0.6,5,6)
f6t6 <- f(0.5,0.6,6,6)

utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
concentrationt6 <- c(0:6)

@@

print(utilityt6)
plot(concentrationt6,utilityt6)

>>>>

$$
U=
\begin{cases}
\frac{x}{np}, & \text{if} \ x \leq np, \\
(2Z-M)+\frac{(M-Z)x}{np}, & otherwise
\end{cases}
$$

@@

$$
U=
\begin{cases}
\frac{x}{np}, & \text{if} \ x \leq np, \\
(2-M)+\frac{(M-1)x}{np}, & otherwise
\end{cases}
$$

The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 8 patches. With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results. To edit in table
^[Not managed to implement Flache's formula on slides, either not understood correctly what it would translate on my formula: p = n number of agents; f = P desired concentration.]\
* With p = 0.2 the right-side of peaked function goes below 0, in sum conditions as p = 0.8 and p = 0.3 utility is approximated above .9 but does not reach 1.

@@

f <- function(p,M,x,n){
  if (x  <= (n*p)){U <- (x/(n*p))}
  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
 # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
  round(U,digits = 3)
 # print(U)
}

@@

f0t8 <- f(0.5,0.6,0,8)
f1t8 <- f(0.5,0.6,1,8)
f2t8 <- f(0.5,0.6,2,8)
f3t8 <- f(0.5,0.6,3,8)
f4t8 <- f(0.5,0.6,4,8)
f5t8 <- f(0.5,0.6,5,8)
f6t8 <- f(0.5,0.6,6,8)
f7t8 <- f(0.5,0.6,7,8)
f8t8 <- f(0.5,0.6,8,8)

utilityt8 <- c(f0t8,f1t8,f2t8,f3t8,f4t8,f5t8,f6t8,f7t8)
concentrationt8 <- c(0:7)

@@

print(utilityt8)
plot(concentrationt8,utilityt8)
